### 2021-07-13 manuscript/manuscript.Rnw
Manuscript update

Cross country scoring: %https://link.springer.com/content/pdf/10.1007/s11127-007-9193-6.pdf

https://link.springer.com/article/10.1007/s11127-017-0494-0

Decathlon scoring: %https://research.ou.nl/en/publications/decathlon-towards-a-balanced-and-sustainable-performance-assessme

@@

\section{Conclusion}

>>>>

Cross country scoring: %https://link.springer.com/content/pdf/10.1007/s11127-007-9193-6.pdf \cite{Hammond2007}

https://link.springer.com/article/10.1007/s11127-017-0494-0 \cite{BoudreauEtAl2018}

Decathlon scoring: %https://research.ou.nl/en/publications/decathlon-towards-a-balanced-and-sustainable-performance-assessme \cit{Westera2006}

@@

\subsections{Simulations}
\subsubsection{uniform ranks}
 - Distributions of points for qualifying and finals given uniform rankings. 
 - Conditional probabilities.  
 \subsubsections{Leave one out analysis} 
 - For n finalists, how often is the ranking preserved when a single climber is removed.  - Independence of Irrelevant groups.  (IIG)

\subsection{Data Analysis} 
\subsubsections{Leave one out analysis} 
 - How would do the ranks changes when a single particpant is removed.  (i.e. What would happed if onyl 5 people made the finals instead of 6 and performance was the exact same?)  (Independence of Irrelevant Alternatives.  (IIA))
 - Examples where you remove the fifth ranked climber from the competition and the medals changed.

 \subsubsection{Correlations}
 - So bouldering and lead as highly correlatd with each other. 
 - As a result bouldering and lead are more highly correlated with overall standings.  
 - Speed climbers are going to suffer under this format.  
 - Speed climbers are getting screwed!

 \subsubsection{Rank Product statistic}
- What does Hannah have?

 Is there manipulability???!?!?!?

outline of paper: 
Simulation stuff.  
Distribution of scores under random ranking. 
Probability of advancement condtional on winnin/losing first event given random ranks.

How different is the rank vs the product.  
Borda count
Voting properties?

\section{Proposed better scoring method}
 - Rank sum
 - Weighted ranks (sum or product)
 -

\section{Conclusion}
- Speed climbers are getting screwed.  
- There is a great dependence on irrelevent party.
